\textbf{NBA Party}

### 2017-07-04 cardinal_analytx_presentation/nightlife_and_sports.tex
Added anecdotal citations.

\begin{frame}   \frametitle{What is the problem?}
  \begin{block}{Do pro athletes party to the detriment of their performance?}
    Anecdotally, yes.\footnote{Cestone ('17), Price ('15), Concepcion ('15), Miller ('15), Campbell ('15).}

@@

  In order to account for jet-lag, we need to be mindful of the direction of travel. We calculate
  \begin{itemize}     \item distance traveled between games,
    \item final direction (bearing) traveling from $a \to b$, and
    \item direction of travel (in east-west degrees) by taking sine.
  \end{itemize}
  Finally, to account for jetlag we interact this east-west measure with travel distance.\footnote{Lallensack ('17)} \end{frame}

>>>>

\begin{frame}   \frametitle{What is the problem?}
  \begin{block}{Do pro athletes party to the detriment of their performance?}
    Anecdotally, yes.\footnote{Duffy ('17), Cestone ('17), Duffy ('16), 
      Price ('15), Concepcion ('15), Miller ('15), Campbell ('15), Ball ('12)}

@@

  In order to account for jet-lag, we need to be mindful of the direction of travel. We calculate
  \begin{itemize}     \item distance traveled between games,
    \item final direction (bearing) traveling from $a \leadsto b$, and
    \item direction of travel (in east-west degrees) by taking sine.
  \end{itemize}
  Finally, to account for jetlag we interact this east-west measure with travel distance.\footnote{Lallensack ('17)} \end{frame}
